### 2017-02-11 data.tex
Adds new paper
Finished some points in the data section

In order to explore the data using the bash tools (cut, grep, etc) and tools
like Python with Pandas, they were exported to a CSV format. Some
transformations may be applied to these files in other to clean useless points
or make the data easier to process.

To begin, each sheet is analysed individually. Conclusions on each list are
registered in the fist section of this chapter.

@@

There is a lot of information in this sheet.

\TODO{Explore}

@@

@@

In order for a student to get approved, some creteria must be followed.

@@

>>>>

In order to explore the data using the bash tools (cut, grep, etc) and tools
like Python with Pandas, they were exported to a CSV format. Some
transformations may be applied to these files in other to clean useless data
points or make the data easier to process.

To begin, each sheet is analysed individually. Conclusions on each list are
registered in the fist section of this chapter. After analysing the original
data, the second section of the chapter asserts which entities and objects are
present in this data. Finally, the third section lists the datasets which
represent those entities and objects.

@@

There is a lot of information in this sheet. Basically, this sheet contains a
big list. That list has a course, a student, and the student's results on that
course. The results contain the grade, if available, if the student was
approved or not, and if not, why? Did he failed the evaluations or simply
missed them?

Some statistics are calculated in a table to the right of this sheet. Those
calculated values are useful, but should be recalculated elsewhere in a later
time if necessary.

@@

\TODO{Some information is missing for this sheet}

@@

In order for a student to get approved, some criteria must be followed. That
criteria is described in the sheet itself.

@@

    \label{tab:results_fetures_enum}
\end{table}
